% !TEX root = ../main.tex

\begin{achievements}

\subsection*{学术论文}

\begin{bibliolist}{00}
  \item Chen, Yongbiao, Sheng Zhang, and Zhengwei Qi. "Maenet: Boosting feature representation for cross-modal person re-identification with pairwise supervision." Proceedings of the 2020 International Conference on Multimedia Retrieval. 2020.
  \item Chen, Yongbiao, et al. "Transhash: Transformer-based hamming hashing for efficient image retrieval." Proceedings of the 2022 International Conference on Multimedia Retrieval. 2022.
  \item Chen, Yongbiao, et al. "DVHN: A Deep Hashing Framework for Large-scale Vehicle Re-identification." arXiv preprint arXiv:2112.04937 (2021).
  \item Liu, Fangxin, et al. "Sstdp: Supervised spike timing dependent plasticity for efficient spiking neural network training." Frontiers in Neuroscience (2021): 1413.
  \item Chen, Yongbiao, et al. "Supervised Contrastive Vehicle Quantization for Efficient Vehicle Retrieval." Proceedings of the 2022 International Conference on Multimedia Retrieval. 2022.
  \item Liu, Fangxin, et al. "Bit-transformer: Transforming bit-level sparsity into higher preformance in reram-based accelerator." 2021 IEEE/ACM International Conference On Computer Aided Design (ICCAD). IEEE, 2021.
  \item Liu, Fangxin, et al. "Sato: spiking neural network acceleration via temporal-oriented dataflow and architecture." Proceedings of the 59th ACM/IEEE Design Automation Conference. 2022.
  \item Liu, Fangxin, et al. "Ebsp: evolving bit sparsity patterns for hardware-friendly inference of quantized deep neural networks." Proceedings of the 59th ACM/IEEE Design Automation Conference. 2022.
  \item Liu, Fangxin, et al. "SoBS-X: Squeeze-Out Bit Sparsity for ReRAM-Crossbar-Based Neural Network Accelerator." IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems 42.1 (2022): 204
  \item Liu, Fangxin, et al. "PIM-DH: ReRAM-based processing-in-memory architecture for deep hashing acceleration." Proceedings of the 59th ACM/IEEE Design Automation Conference. 2022.
\end{bibliolist}

% \begin{bibliolist*}{00}
%   \item 第一作者. 中文核心期刊论文, 2007.
%   \item 第一作者. EI 国际会议论文, 2006.
% \end{bibliolist*}

% \subsection*{专利}

% \begin{bibliolist}{00}
%   \item 第一发明人，“永动机”，专利申请号202510149890.0
% \end{bibliolist}

% \begin{bibliolist*}{00}
%   \item 第一发明人，“永动机”，专利申请号XXXXXXXXXXXX.X
% \end{bibliolist*}

\end{achievements}
